Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-03-11 paper.tex
Add corrections for the polarizability

electronic contribution to the dielectric constant where the dipole
$\boldsymbol{P}$ comes from the displacement of electron cloud under
external electric field. For the majority of the 2D nanosheets, the

@@

@@

Simulations were carried out using plane-wave density functional
theory package VASP
\cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2} using the projector
augmented wave (PAW) approach with GW pseudopotentials
\cite{Kresse_1999_pseudopotentials}. Band gaps were calculated using
the Heyd-Scuseria-Ernzerhof hybrid functional (HSE06)
\cite{Heyd_2003,HSE_2006}, with spin orbit coupling (SOC) explicitly
included. The geometries were converged both in cell parameters and
ionic positions, with forces below 0.04 eV/\AA. To ensure the accuracy
of dielectric property of monolayer, a vacuum spacing of $>$ 15 \AA~is
used. A k-point grid of \(7\times7\times1\) was used to relax the
superlattice, with an initial relaxation carried out at the
Perdew-Burke-Ernzerhof
(PBE)\cite{Perdew_1996,Ernzerhof_1999,Paier_2005_PBE}
exchange-correlation functional level and a subsequent relaxation
carried out at HSE06 level, allowing both cell parameters and ionic
positions to relax each time. In VASP, the tag PREC=High was used,
giving a plane wave kinetic energy cutoff of 30\% greater than the
highest given in the pseudopotentials used in each material. This 
guarantees that absolute energies were converged to a few meV and
the stress tensor to within 0.01 kBar.  Calculation of the
macroscopic ion-clamped dielectric tensor were carried out with an
18$\times$18$\times$1 k-grid and electric field strength of 0.001
eV/\AA. The materials from Ref.\citenum{Haastrup_2018} for comparison
were choses with the GW bandgap larger than 0.05 eV. Bulk layered
materials were constructed by relaxing the c-axis length of
corresponding monolayer material with the interlayer van der Waals
(vdW) interactions calculated by non-local vdW correlation
functional\cite{Lee_2010_vdFD2}.  The dielectric properties of bulk
layered materials using VASP were calculated at HSE06 level with
18$\times$18$\times$6 k-grid with same parameter as for monolayer,
while the dielectric properties of bulk counterparts of Ref.~\citenum{Haastrup_2018}
are calculated at PBE level with a k-point density of 10~\AA$^{-1}$.

>>>>

electronic contribution to the macroscopic dielectric constant where
the dipole $\boldsymbol{P}$ comes from the displacement of electron
cloud under external electric field, while the ionic contribution
\cite{Laturia_2018} ($\boldsymbol{P}$ comes from the displacement of
nuclei) to the static $\varepsilon$ is considered.
For the majority of the 2D nanosheets, the

@@

Note due to the choice of $\varepsilon$ is limited to the electronic
macroscopic dielectric constant, $\alpha_{\mathrm{2D}}$ naturally
refers to the electronic polarizability (the polarizability of the
electron cloud \cite{Israelachvili_2011}).

@@

Simulations were carried out using plane-wave density functional
theory package VASP \cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2}
using the projector augmented wave (PAW) approach with GW
pseudopotentials \cite{Kresse_1999_pseudopotentials}. Band gaps were
calculated using the Heyd-Scuseria-Ernzerhof hybrid functional (HSE06)
\cite{Heyd_2003,HSE_2006}, with spin orbit coupling (SOC) explicitly
included. The geometries were converged both in cell parameters and
ionic positions, with forces below 0.04 eV/\AA. To ensure the accuracy
of dielectric property of monolayer, a vacuum spacing of $>$ 15 \AA~is
used. A k-point grid of \(7\times7\times1\) was used to relax the
superlattice, with an initial relaxation carried out at the
Perdew-Burke-Ernzerhof
(PBE)\cite{Perdew_1996,Ernzerhof_1999,Paier_2005_PBE}
exchange-correlation functional level and a subsequent relaxation
carried out at HSE06 level, allowing both cell parameters and ionic
positions to relax each time. In VASP, the tag PREC=High was used,
giving a plane wave kinetic energy cutoff of 30\% greater than the
highest given in the pseudopotentials used in each material. This
guarantees that absolute energies were converged to a few meV and the
stress tensor to within 0.01 kBar.  Calculation of the macroscopic
ion-clamped dielectric tensor were carried out with an
18$\times$18$\times$1 k-grid and electric field strength of 0.001
eV/\AA.  Local field effect corrections are included at the
exchange-correlation potential $V_{\mathrm{xc}}$ at both PBE and HSE06
levels. The materials from Ref.\citenum{Haastrup_2018} for comparison
were choses with the GW bandgap larger than 0.05 eV. Bulk layered
materials were constructed by relaxing the c-axis length of
corresponding monolayer material with the interlayer van der Waals
(vdW) interactions calculated by non-local vdW correlation
functional\cite{Lee_2010_vdFD2}.  The dielectric properties of bulk
layered materials using VASP were calculated at HSE06 level with
18$\times$18$\times$6 k-grid with same parameter as for monolayer,
while the dielectric properties of bulk counterparts of
Ref.~\citenum{Haastrup_2018} are calculated at PBE level with a
k-point density of 10~\AA$^{-1}$. Local field effect corrections are
also used for the dielectric properties of bulk systems.
